Palomar 5 Gaps

### 2024-09-30 paper/main.tex
updated spacing
updating the statistics

    The clusters that impacted Palomar 5's stream in our simulations are presented in Fig.~\ref{fig:histogram_impact_time}, along with when they impacted the stream. First, there are few impacts that happen early on in the simulation. This is not surprising, as it the tidal tails are smaller and thus there is less volume to be perturbed. Next, is that 44/50 simulations contain a visible gap from NGC2808, all of the encounters occuring about 200~Myr ago. This is so much more than any other peak that we broke the scale of the histogram. The reason is that the uncertainty in the precise position of the clusters along their orbits grows in look back time. Since this encounter is recent, most of the sampled initial conditions give rise to a significant enough impact in the stream that causes a gap.

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{histogram_impact_time.png}
      \caption{When the impacts occured}
      \label{fig:histogram_impact_time}
      \end{figure*}

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present three different graphs in Fig.~\ref{fig:mass_size_plane}. The top plot shows the angular momentm and energy plane. The

    - to no surprise, you have to come within Palomar 5's orbital space

>>>>

    The clusters that impacted Palomar 5's stream in our simulations are presented in Fig.~\ref{fig:histogram_impact_time}, along with when they impacted the stream. First, there are few impacts that happen early on in the simulation. This is not surprising, as it the tidal tails are smaller and thus there is less volume to be perturbed. Next, is that 44/50 simulations contain a visible gap from NGC2808, all of the encounters occuring about 200~Myr ago. This is so much more than any other peak that we broke the scale of the histogram so that this peak would not dwarf the significance of all others. The reason is that the uncertainty in the precise position of the clusters along their orbits grows in look back time. Since this encounter is recent, most of the sampled initial conditions give rise to a significant enough impact in the stream that causes a gap.

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{histogram_impact_time.png}
      \caption{The time of impact for each flyby that caused a gap. Each cluster is given a consistent and unique color. The scale of the histogram is broken between 8 and 42 since the gaps from NGC~2808 are in a league of their own with respect to other clusters.}
      \label{fig:histogram_impact_time}
      \end{figure*}

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present three different graphs in Fig.~\ref{fig:mass_size_plane}. The top plot shows the angular momentm and energy plane. To no surprise, the globular clusters that perturb Palomar 5 are within a band of energy enclosed the energy of Palomar 5. This indicates that a cluster's orbital space needs to overlap with Palomar 5's. There appears not to be a preference in angular momentum. Note that in this panel all initial conditions for the clusters are plotted. Clusters of gray dots indicate the same cluster. However, for the least bound milky way clusters, the uncertainties in distances and motions allow for a wide range of energies, prograde and retrograde orbits. These are Crater, Palomar X and Eridanus. This is consistent with Vasiliev et al 2021, yet not very significant for this study since they do not influence Palomar 5 and could have been ignored.

    Next, in the middle panel of Fig.~\ref{fig:mass_size_plane} we view the mass size plane. The
